---
title: "Analyzing Worldwide Suicide Rates Over Time"
author: "Michael Huang"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)
library(ggplot2)
library(knitr)
library(plotly)
source("analysis.R")
```

## Introduction

Include an introduction that describes the time series, answering the following questions: When was the data collected? Where was the data collected? Who collected the data?  Why was the data collected?

The data was collected from the years
The data was collected from 
The source of the data was , and it was collected because

## Data Graphics

```{r pressure, echo=FALSE}
plot(pressure)
```

Include a plot of the time series data, which includes a caption, labeled axes, and a legend if needed. 

The plot above shows the data, 

## Discussion

Include a discussion of what can be learned from the time series, what stakeholders might be impacted by the time series, and how it might be used to do good in the world. What, in short, do you conclude from your analysis?

From the time series data, we can see that
Some example stakeholders that might be impacted by the time series
One way to draw the good from this is to 
From our analysis, we can conclude that

## Reflection

Include a reflection on what you learned from your analysis of the time series data.  You might answer such questions as: What did you learn? What new questions do you have?

I learned
Some new questions that arose when reflecting upon the results included 

## Code

#### analysis.r


``````{r, eval=FALSE, code=readLines("./analysis.R")}
```