---
title: "Analyzing Worldwide Suicide Rates Over Time"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)
library(ggplot2)
library(knitr)
library(plotly)
source("analysis.R")
```

## Introduction

This dataset is a massive dataset describing suicide numbers, rates, and general socioeconomic data for every country from 1985-2026.  

The data was compiled from a variety of sources. These include the United Nations (via their Development Program), the World Bank, and the World Health Organization. Most of the data was collected for the purpose of developing human resources and promoting societal and international development (especially in the case of the United Nations and the World Bank), or to raise awareness and promote social health (especially in the case of the World Health Organization).

## Data Graphics

``` {r echo = FALSE, message = FALSE}
by_year
```

Include a plot of the time series data, which includes a caption, labeled axes, and a legend if needed.  

The plot above shows the data,  

Looking at the US data, it closely follows with the global trends:

``` {r echo = FALSE, message = FALSE}
by_year_us
```

Some other interesting graphs, with the worldwide generational data first and then the corresponding US data:

``` {r echo = FALSE, message = FALSE}
by_gen
by_gen_us
```

Some other interesting graphs for the US, showing suicide rates by age and by sex:

``` {r echo = FALSE, message = FALSE}
by_age_us
by_sex_us
```

## Discussion

From the time series data, we can see a trend in how  

Some example stakeholders that might be impacted by the time series is the rates at which suicide has changed among the different generations, or how suicide affects people of different development levels or generations.   

One way to draw the good from this is to analyze this further using more specific economic data. Although we do have measures such as GDP and HDI, we probably can look more specifically to pinpoint specific trends and root causes that might predict or suggest targets for suicide prevention. We can try to find and subsequently develop more effective indicators and preventors for suicide in this way.  

From our analysis, we can conclude that suicide  

## Reflection

Include a reflection on what you learned from your analysis of the time series data.  You might answer such questions as: What did you learn? What new questions do you have?  

I learned about  

Some new questions that arose when reflecting upon the results included how other cultural aspects or specific environments (e.g. urban, rural) affect suicide rates. As country-wide data is fairly generalized and very broad, it isn't really fair to draw conclusions from across this data, and generalizing a generation using multiple cultures and countries feels inaccurate as well.  

## Code

#### analysis.r


``````{r, eval=FALSE, code=readLines("./analysis.R")}
```